\section{Expert assessment}
\subsection{Process }
\subsubsection{Assessment process}

\bigskip

{\textbullet} The openETCS documents from the development process should be made available to the assessor. All
documents should be submitted and needs to be reviewed for content and form by the assessor as well as reflected and
evaluated in the project life cycle and CENELEC standard EN 50128. The results should continually be relayed to the
responsible entities within the WPs.

{\textbullet} Due to the agile workflow in the openETCS project this assessment process should be done iteratively.


\bigskip

\subsubsection{Review of Planning Documents}
{\textbullet} The planning documents for quality assurance (software quality assurance plan, software verification plan,
software validation plan, software coding standards, software configuration management plan and software maintenance
plan) should be reviewed for changes. Also the deliverables should be reviewed for plausibility and compliance with
standards.

{\textbullet} The unresolved issues of the deliverables review shall be discussed.

{\textbullet} Measures shall be defined.

{\textbullet} A review report needs to be created


\bigskip


\bigskip

\subsubsection{Initial Assessment }
\liststyleLv
\begin{itemize}
\item Here a brief description of the start date of the Assessment process as it is described in the Assessment Plan. 
\end{itemize}
\subsection{Sections assessed}
{\textbullet} Here the assessed sections of the life-cycle of the SW development EN 50128 should be presented.

{\textbullet} Suggestion:

\begin{itemize}
\item Table with sections of the SW life-cycle and a column with Yes/No Statement 
\end{itemize}